---
title: "P8105_hw1_wl3013"
author: "Wen Li (wl3013)"
date: "2025-09-13"
output: github_document
---

# Problem 1

```{r setup, include=FALSE}
#install.packages("moderndive")
library(moderndive)
library(ggplot2)
library(tidyverse)
```


```{r, echo=FALSE}
data("early_january_weather")
```

* View variables in this dataset & check the values of important variable
```{r}
names(early_january_weather)
summary(early_january_weather)
```


* Show the size of the dataset, including the number of row and column.
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
 Row = 358, column = 15.

* Calculate the mean of temperature
```{r}
mean(early_january_weather$temp)
```


Summary: 
  This dataset has 358 rows and 15 columns. 
  The variables inclue "origin", "year", "month", "day", "hour", "temp", "dewp", "humid", "wind_dir", "wind_speed", "wind_gust",  "precip", "pressure", "visib", "time_hour". 
  The mean of temperature is 39.58 °F.

* Creat the scatterplot & Save it
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid) ) + 
  geom_point() + 
  labs(
    title = "Temperature vs. Time",
    x = "Time (Hour)",
    y = "Temperature (°F)"
  )
ggsave("Scatter_temp_time.png", width = 7, height = 5)
```

# Problem 2

*Create a data frame contains:
  A random sample of size 10 from standard Normal distribution
  Logical vector indicating whether elements of the sample are greater than 0
  Character vector of length 10
  Factor vector of length 10, with 3 different factor "level"

```{r}
set.seed(123)

Q2_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = rnorm(10)>0,
  vec_char = sample(letters,10),
  vec_factor = factor(sample(c("Yes","No","Unknown"),10, replace = T))
  
)
```


*Try to take the mean of each variable

```{r}
mean(Q2_df %>% pull(vec_numeric))
mean(Q2_df %>% pull(vec_logical))
mean(Q2_df %>% pull(vec_char))
mean(Q2_df %>% pull(vec_factor))
```
Summary: Taking mean only work for variable of numeric and logical, the other two, character vector and factor vector can't be calculate the mean.

```{r,include=FALSE}
# Turn vec_logical, vec_char and vec_factor into numeric
as.numeric(Q2_df %>% pull(vec_logical))
as.numeric(Q2_df %>% pull(vec_char))
as.numeric(Q2_df %>% pull(vec_factor))

# Try to take the mean again
mean(Q2_df %>% pull(vec_logical))
mean(Q2_df %>% pull(vec_char))
mean(Q2_df %>% pull(vec_factor))

# This works for logical vector, but not for the other two. Character vector and factor vector still return NA when calculating the mean. 
```

